
\subsection{Team Project Topic Summary} 
Group 2 is currently working on a project to introduce several programming languages to young adults. The target audience consists of graduating high school seniors and incoming college freshmen. The presentation will provide a high-level overview of the following programming languages: C++, Python, R, and Java. Each language will be presented with the same template: which includes the history/background, uses, and libraries/communities.

\subsection{Audience and Purpose}
The purpose of this presentation is to provide exposure to prospective students who are interested in pursuing a career in the technology industry. By providing an overview of each programming language, we aim to give them a better idea of what to expect and help them decide which language(s) to use in their future studies or career. Our goal is to provide a starting point for these students to explore and understand the basics of different programming languages, and encourage them to continue their learning journey beyond this presentation.

\subsection{Background Information}
We believe that this educational content is warranted for our intended audience, as it can provide them with the foundational knowledge they need to succeed in the technology industry. By presenting this content in a clear and accessible manner, we hope to spark their interest in programming and encourage them to continue their learning journey beyond this presentation.

\subsection{Materials Needed}
The materials needed for this presentation are a computer or device that can display a PowerPoint presentation, and an internet connection to access online resources. There are no additional materials required for this presentation, as it is designed to be an introductory overview of programming languages. 

\subsection{Video Production and Editing}
For video production, we hope to work asynchronously, with each team member recording themselves presenting their sections of the PowerPoint whilst following guidelines specified by module documents. After each member records their respective parts, we will stitch and edit all four recordings into one combined video.

\subsection{Document/Video Text}
The next following sections will be topics outlined and discussed on our presentation. Structurally,  we will provide an introduction then segway into our main topics, that is, four programming languages (each presented by a different team members).
%\\


